Water resource utilization regimes at a basin scale: transition framework and development traps

### 2020-08-03 tex/Main Text/manuscript.tex
写完结果第三段

\section*{Results}
%tag 结果1: 指数划分结构
\subsection*{Water utilization regimes}
% 这一节主要展示BCDI的变化趋势和WUR的划分
By the two significantly detected change points,
the changes of IWRU index are split into three periods, 
whose slopes are various and mainly contributed by different factors (Figure~\ref{fig:IWRU}).
\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/index.pdf}
	\caption{Changes of the IWRU index. 
	\textbf{A,} with two change points in 1978 and 1994, three periods were detected in trend of the IWRU.
	\textbf{B,} changes of IWRU in three periods have various slopes, while the second period have a negative growths rate.
	\textbf{C,} changes of the IWRU within three certain periods, which have different main contributors.
	}
	\label{fig:IWRU}
\end{figure}
% 接下来分句介绍每个阶段的特征
% 第一阶段
In the first period (P1, 1965-1978), the IWRU index had a rapidly increasing 
and the lightening of water stresses made the most striking contribution (124\%), 
while tendentiousness and pattern of the water utilization had slight negative contribution.
% 第二阶段
In the second period (P2, 1979-1994), the IWRU index experienced a slight drop, 
despite positive contributions of tendentiousness and pattern of water utilization,
because of increasing stresses on water resource playing a larger negative role (-146\%). 
% 第三阶段
However, as the further increasing of positive contributions of water utilization tendentiousness and pattern, 
and decelerations of water stresses in the third period (P3, 1995-2013), a positive growth of the IWRU returned.
% 总而言之，每个阶段都由水资源利用的不同维度提供最大的正向作用
As a result, each period is various in the most striking positive contributors to IWRU, 
corresponding to different dimensions of water utilization.

@@

%tag 结果2
\subsection*{Changes between different regimes}
% 在不同的维度下各阶段进行对比，可以发现不同的水资源利用体系间存在明显差异。
A comparison of the phases under different dimensions reveals notable differences between each water use regime 
(Figure~\ref{fig:dimensions}).
\begin{figure*}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/dimensions.pdf}
	\caption{
		Changes in different dimensions of water resources utilization regime.
		\textbf{A,} changes of scarcity-flexibility-variability water stresses index (SFV-index).
		\textbf{B,} changes of non-provisioning water share, indicating water utilization tendentiousness.
		\textbf{C,} changes of water utilization pattern index.
		}
		\label{fig:dimensions}
	\end{figure*}
% 从阶段一到阶段二，水资源压力的变化最为明显
Moving from the regime in P1 to P2, the most striking change is the reversal of the trend in water stresses (Figure~\ref{fig:dimensions}A).
% 由于水资源压力由稀缺性、灵活性和变异性共同决定，P1-P2的变化主要看SFV
The P1, when water resources were the most abundant period, also had the least water consumption, 
while most of which were flexible water utilization.
Despite the rapid rise in water use during that period, numerous reservoirs were also built during this period, 
which increased storage capacities in each water-demand region to relief water resource stresses (SI).
However, entering P2, although water consumptions continued to increase, 
the number of new reservoirs was significantly reduced and the total storage capacity of each region was hardly increasing any more. 
Coupled with declining natural water resources, the water stress index of the basin was rapidly increasing.
% 另一方面，P2-P3，持续变化的水资源利用倾向与格局
On the other hand, as the most positive contributors to the IWRU index in P2 and P3, separately, 
tendentiousness and patterns of water utilization were still enlarging their impacts (Figure~\ref{fig:dimensions}B and C). 
% 首先是用水比例的变化
Representing tendentiousness of water utilization, 
increasing non-provisioning share of water utilization were mainly contributed by larger industrial water consumptions and minor total water uses, 
while the influence of both is waning.
% 再讨论用水格局的变化
However, patterns of water utilization, with accelerating changes and larger contributions to the IWRU, 
were mainly benefited from the convergence of development paces between regions and the basin-wide intersectoral water balance.
% 最后，每个阶段起
In summary, the changes in various aspects of the water use characteristics of the Yellow River Basin over the past 60 years 
are reflected in the changes in the corresponding indicators of the three dimensions.

\subsection*{Drivers of regime shifts}
Based on our model, two regime shifts had distinct main drivers.
% 第一个 regime shift 主要是经济总量提升导致资源耗竭的加速。
%经济总量对用水量预测的能力，经济总量对水资源压力的预测能力。
%经济总量+水库修建对水量、水资源压力的预测
% 第二次 regime shift 发生了用水关系的变化

>>>>

\section*{Results}
\subsection*{Division of Water utilization regimes}
% 这一节主要展示IWRU的变化趋势和WUR的划分
By the two significantly detected change points,
the changes of IWRU index are split into three periods, 
whose slopes are various and mainly contributed by different factors (Figure~\ref{fig:IWRU}).
\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/index.pdf}
	\caption{Changes of the IWRU index. 
	\textbf{A,} with two change points in 1978 and 1994, three periods were detected in trend of the IWRU.
	\textbf{B,} changes of IWRU in three periods have various slopes, while the second period have a negative growths rate.
	\textbf{C,} changes of the IWRU within three certain periods, which have different main contributors.
	}
	\label{fig:IWRU}
\end{figure}
% 接下来分句介绍每个阶段的特征
% 第一阶段
In the first period (P1, 1965-1978), the IWRU index had a rapidly increasing 
and the lightening of water stresses made the most striking contribution (124\%), 
while tendentiousness and pattern of the water utilization had slight negative contribution.
% 第二阶段
In the second period (P2, 1979-1994), the IWRU index experienced a slight drop, 
despite positive contributions of tendentiousness and pattern of water utilization,
because of increasing stresses on water resource playing a larger negative role (-146\%). 
% 第三阶段
However, as the further increasing of positive contributions of water utilization tendentiousness and pattern, 
and decelerations of water stresses in the third period (P3, 1995-2013), a positive growth of the IWRU returned.
% 总而言之，每个阶段都由水资源利用的不同维度提供最大的正向作用
As a result, each period is various in the most striking positive contributors to IWRU, 
corresponding to different dimensions of water utilization.

@@

%tag 结果2
\subsection*{Changes of water utilization between regimes}
% 在不同的维度下各阶段进行对比，可以发现不同的水资源利用体系间存在明显差异。
A comparison of the phases under different dimensions reveals notable differences regarding water utilization
between each water use regime (Figure~\ref{fig:dimensions}).
\begin{figure*}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/dimensions.pdf}
	\caption{
		Changes in different dimensions of water resources utilization regime.
		\textbf{A,} changes of scarcity-flexibility-variability water stresses index (SFV-index).
		\textbf{B,} changes of non-provisioning water share, indicating water utilization tendentiousness.
		\textbf{C,} changes of water utilization pattern index.
		}
		\label{fig:dimensions}
	\end{figure*}
% 从阶段一到阶段二，水资源压力的变化最为明显
Moving from the regime in P1 to P2, the most striking change is the reversal of the trend in water stresses (Figure~\ref{fig:dimensions}A).
% 由于水资源压力由稀缺性、灵活性和变异性共同决定，P1-P2的变化主要看SFV
The P1, when water resources were the most abundant period, also had the least water consumption, 
while most of which were flexible water utilization.
Despite the rapid rise in water use during that period, numerous reservoirs were also built during this period, 
which increased storage capacities in each water-demand region to relief water resource stresses (SI).
However, entering P2, although water consumptions continued to increase, 
the number of new reservoirs was significantly reduced and the total storage capacity of each region was hardly increasing any more. 
Coupled with declining natural water resources, the water stress index of the basin was rapidly increasing.
% 另一方面，P2-P3，持续变化的水资源利用倾向与格局
On the other hand, as the most positive contributors to the IWRU index in P2 and P3, separately, 
tendentiousness and patterns of water utilization were still enlarging their impacts (Figure~\ref{fig:dimensions}B and C). 
% 首先是用水比例的变化
Representing tendentiousness of water utilization, 
increasing non-provisioning share of water utilization were mainly contributed by larger industrial water consumptions and minor total water uses, 
while the influence of both is waning.
% 再讨论用水格局的变化
However, patterns of water utilization, with accelerating changes and larger contributions to the IWRU, 
were mainly benefited from the convergence of development paces between regions and the basin-wide intersectoral water balance.
% 最后，每个阶段起
In summary, the changes in various aspects of the water use characteristics of the Yellow River Basin over the past 60 years 
are reflected in the changes in the corresponding indicators of the three dimensions.

\subsection*{Causes of water utilization regime changes}
Some main drivers caused the changes of water utilization regime.
% 经济总量提升导致资源耗竭的加速。
(1) The expansion of irrigated area and the economic growth of industry and services are key to the
changes in the tendentiousness of water utilization in P1 and P2.
During P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of xx/year, 
and agriculture was the dominant water use (xx \% of the total).
After entering P2 to P3, however, while the expansion of irrigated area stalled, 
industry and services gradually took off, which took up more water resources.
% 用水关系的变化
(2) Efficiency of water use sparkly changed during the P3.
Although both industrial services output and irrigated agricultural area resumed expansion in P3, 
both their output per unit and water consumption per unit area experienced significant declines.
% 不断变化的管理模式。
(3) Changing water management practice contributed between different periods.
In P1, most of the reservoirs are built in regions where water use is growing, 
and the trend of growth in storage capacity and growth in water demand remain relatively consistent regionally.
In P2, on the other hand, the number of additional reservoirs decreases significantly. 
In P3, the number of reservoirs increases significantly again, 
but the growth of storage capacity does not match the growth of water demand.
